Review of Edge Detectors

### 2014-05-26 review/review_answer_2.tex

\newcounter{myquestion}
\newcommand{\ml}{\mathcal{L}}
\newcommand{\ms}{\mathcal{S}}

\begin{document}
\maketitle

%\begin{abstract}
%\end{abstract}

\chapter{Introduction}
In this communication we answer to the second rounds of review of the article "A Contrario Selection of Optimal Partitions for Image Segmentation", submitted to the SIAM Journal on Imaging Sciences.
In the first place, we would like to thank again the reviewers for the detailed and thoughtful review provided. In the following we address the issues raised by the reviewers. For each issue, an answer is provided and a cross-reference with a red tag $C_n$ (where n is the number of the correction) to the corresponding (corrected) part of the paper is provided. In addition, changes made to the paper are highlighted in red (when significative) in the new version of the paper. 
These red marks will be removed for the final version.

@@

\que In general the paper provides all the information necessary. Some parts need nevertheless rewriting either because of minor mistakes (that make some sentences really hard to read) or because of mathematical inaccuracies.\\

\ans We thank the reviewer for the comments and for contributing to improve the quality of the paper. We did a major proof-reading of the paper and we did our best effort to improve the writing.\\

\que You mention a video but it was not included in the supplementary les (35-757-1-SP.zip and 35-758-1-SP.zip) so that I could not see it.\\

\ans we removed the videos from the submission, they are nice to see, but not so relevant.\\

@@

\ans Corrected in \ref{correction_a:first_derivative:sobel} and \ref{correction_a:first_derivative:sobel}.\\

\que "thus It"\\

\ans Fixed\\

\que "As mentioned before this leads to ab overdetermied"
\ans Fixed\\

\que "Gaussian kernel is generated by sampling the"\\
\ans YY\\
\que "unlike the case of Gaussian kernel"\\
\ans Suggested a partial correction\\

\que "are not independent of each one"\\
\ans  Rephrased\\
\que "implies complete the borders with many zero valued pixels as needed"\\
\ans Rephrased\\
\que "It can be seen in Figure 16 an area of interest of the image."\\
\ans Fixed\\
\que "appearing unwanted isolated edges"\\
\ans Fixd\\
\que "because they only consists"\\
\ans Fixed\\
\que "more fair"\\
\ans Fixed\\

\que "runs significative faster"\\
\ans Fixed\\

@@

Once again the two algorithms differs mainly in the way of computing
derivatives. The former rely on the filtering with laplacian of gaussian or on
the filtering with a gaussian followed by a laplacian operator. The latter
relies on a local bicubic approximation followed by a second derivative
analytical computation. Sufficient details are again provided along with
algorithmic description. However some of the details could be made clearer (see
later comments).

The fourth section provides technical details on some filtering aspects and the
last section is dedicated to the experimental discussion.

\subsection{Detailed comments, typos and typesetting}
\subsubsection{Demo}
The url \url{http://dev.ipol.im/~haldos/ipol_demo/xxx_edges/} provided in the preprint
contains a broken demo. This is not very important though since the demo code
provided in the submission works correctly and it should eventually replace the
one specified in the pdf.

\subsubsection{ Section 2.3: The Sobel operators}
\que No upper case on the "i" of "thus It".

\ans Corrected.\\

\subsubsection{Section 2.4: Computation of the edges}
\que The threshold variable "th" should be in italic.
Missing a "." at the end of the section.\\

\ans Corrected.\\

\subsubsection{Algorithm 2:}
\que
\begin{verbatim}
tzc" --> "th_{ZC}"
\end{verbatim}

\ans Changed as suggested.\\

@@

\que Using the expression "polar form" is completely misleading since theta is
fixed. Haralick simply considers the second derivative in the direction of the
gradient and there comes the restriction $f_\theta(\rho)$ of the polynomial
approximant to the line of angle theta.\\

\ans Changed, see \refc{second_derivative:haralick:analitical:derivative}. We now explicitely defined the line of angle theta, and described the points lying on that line in terms of $\rho$ and $\theta$\\

\que Equation 3.9 is not mathematically correct. You should add before it, $\exists
\rho\in[0,\rho_0]$ s.t. Equation 9.\\

\ans We rewrote the whole section, taking this comment into account.\\

@@

\que I would integrate the footnote 7 within the text, just after: "This parameter
must be greater than zero and less
than 1." since it provides the rationale behind these constraints.\\

\ans Done, see \refc{second_derivative:haralick:analitical:parameter_value}.\\

\que You should explain what you mean by the optimal value of $\rho_0$. If you are
simply referring to Haralick's claims, you should state it explicitly.\\

\ans We actually used those values inspired on other works, and tested them experimentally. To do this properly we should benchmark this parameter against a proper database, and see what's best. From our point of view, that kind of work is outside the scope of this paper.\\

\que Also, are you sure you implement the exact conditions specified in the
original article by Haralick. The ones I could find are as follows:
"If for some $\rho, |\rho|\leq\rho_0, [...], f"_\alpha(\rho)<0$ [eq.1],
$f''_alpha(\rho)=0 [eq.2] and f'(\rho)\neq 0$ [eq.3] we have discovered [...]"
I guess that [eq.1] was meant to involve a third derivative instead of a second
derivative. Then it is exacly your condition $c_3<0$. I don't find anything
close to [eq.3] in your description. Besides, although (as you justified it)
[eq.2] implies your condition $|\frac{C_2}{3C_3}|\leq\rho_0$ they are not
equivalent. I would say that you should add that $C_2$ must be positive as well. If you want to stick with your conditions only, you should at least add a discussion pointing on the fact that they differ from the one formulated by Haralick, and
describe the differences. I actually tried changing your code to take the
sign of $C_2$ into account and to introduce [eq.3]: it does not seem to change
the output. Yet I would recommend that you investigate why and provide that
information.\\

\ans Yes, we verified again the conditions and we are implementing exactly Haralick's conditions. Regarding [eq. 1], indeed there is a typo in Haralick's paper. We explained that in \refc{second_derivative:haralick:analitical:condition} in a footnote.
Regarding [eq. 2], I think the explanation was confusing and we also made a mistake assuming $\rho>0$. if you lift that assumption and taking into account that the exact solution of $f''=0$ is $\rho^*=-\frac{C_2}{3C_3}$, our condition is exactly what it reads in Haralick's paper $\rho<\rho_0$. I think with the new presentation this should be clearer. Starting with \refc{second_derivative:haralick:analitical:conditions}, we rewrote the whole section.\\

\subsubsection{ Section 4: Common Mathematical Operations}
\que "All algorithms implemented" --> "All implemented algorithms"''\\
\ans Corrected.\\

\subsubsection{ Figure 11:}
\que "Is clearly required" --> "It ..."\\

\ans Rephrased.\\

\que The text in the figure is practically unreadable.\\
\ans Enlarged figure.\\

@@

\que You use too many short paragraphs!! This is true in general for your text, but
it is especially pronounced here. I would recommend one paragraph for the synthetic example and one or two for the windmill example.\\

\ans We corrected this, thanks.\\

\que Also, I don't see the point of duplicating the execution time data, once in the figures and another time in a dedicated table.\\

\ans Since we don't have any space restrictions, summarizing all execution times in a table, will help the reader compare them directly. \\

@@

I am not entirely convinced by your explanation of the thicker edges in
Haralick case. There are two reasons form my doubts:
- My first point is that even with a smooth model, the fact that the detection
is based on zero-crossing of second derivative should make the detection well localized. Indeed when dealing with a smooth edge, on the contrary to the
first derivative methods, zero-crossing is supposed to fire only at the
location of maximum gradient.
- Then, taking the opposite view to your argument, imagine that you would fit a more regular polynomial, let's say of degree 4. Then instead of getting a
smoother approximant, I imagine that you would witness some kind of Runge's
phenomenon which would translate in ringing patterns that would make the edge detection less predictable. It may be that the reason of the thicker edges is precisely the ringing that would create many local edges. But I must say that
this is only a lead and I am not sure of this explanation either. You could
challenge this argument on the synthetic example by plotting the profiles of
the function $f_theta(rho)$ at few edge locations.

\subsubsection{ Section 6: Conclusion}
\que Your conclusion is quite poor. It simply recaps what was just stated in the
experimental section. You could try to improve it by placing the
algorithms under study in a broader context. The only part of your conclusion
that follows that path is the reference to Canny's approach. Much more
works have been made on edge detection since then, for instance approaches
based on machine learning that have several advantages to be discussed. This one option among others.\\

\ans We disagree on this. The conclusions depend on the focus you want to give to the article. This article is about reproducing basic edge detectors, and briefly compare them. It is not a survey not a benchmark of every possible edge detector. As contribution for IPOL, we think we might add some basic blocks like this one, and once there is a considerable base of papers devoted to edge detection, we might add one publication devoted to put them into a broader context. We'd rather keep this publication narrow focused on the subject.\\

\que Again, too many short paragraphs.\\

\ans Tried to improve that along the paper.\\

@@

\section{ Comments on the Code and demo}

\subsubsection{General description of the code}
The reviewed code consists of two files: edges.c contains the main function,
while the actual algorithms are included in \verb+classic_edge_detectors.c+; This
latter contains several routines:
- 6 routines are dedicated to each algorithms or their different flavors.
Accordingly one can find the following routines:
\begin{verbatim}
+ edges_roberts
+ edges_prewitt
+ edges_sobel
+ edges_mh for the Marr-Hildreth algorithms with gaussian and laplacian
+ edges_mh_log for the same algorithm with the laplacian of gaussian
+ edges_haralick
- another routine called conv2d implements image filtering with a squared kernel
- eventually two other are responsible for generating a gaussian kernel or laplacian of
gaussian
\end{verbatim}

The implementations of all the detectors match faithfully their description in
the pdf. This is obviously a very good point. I checked as carefully as I could
all the kernel entries. This was quite some fun concerning Haralick's mask!
Although in this case I only checked that the entries were identical in the pdf
and the code (I did not check the mathematical validity of those entries).

\que Consistently to my expectation, the three routines corresponding to first order
derivative (robert, prewitt and sobel) are strictly identical (except for
names of variables and the kernel entries). One could argue that this property,
that is quite clear in the paper, should have been reflected in the code. Yet I
would understand that the authors prefer to keep the three routines independent
from one another.\\

Similarly, the two routines implementing the two flavors of the Marr-Hildreth
detector are entirely identical a part from the filtering phase. Again both
implementation could be merged into a single routine.\\

\ans Indeed as they are different algorithms we rather keep separate implementations, although we agree that it might not be the best practice from the software point of view.\\

\subsection{ Algorithm's parameters}
\que From the article I could retrieve the following list of parameters:
\begin{verbatim}
- First order methods : th
- Marr-Hildreth: sigma, n, $th_{ZC}$
- Haralick: $ro_0$
- All algorithms: padding methods
\end{verbatim}
They corresponds exactly to the ones present in the code and (except for the
padding method) also those exposed in the demo. This is quite satisfying!

\ans Thanks for the comment. We added the padding method as an input parameter of the algorithm in the code (not in the demo).\\

\subsection{ Minor comments}
\subsubsection{ In gaussian\_kernel}
\que The normalization by the sum is different from the one evoked in Section
4.1.1. You should either change the implementation or comment on this in the article. Note
also that the comment in the code correspond to the formula in the pdf instead of the implemented one.\\

\ans Corrected, now  the code uses the PDF formula\\

@@

\subsubsection{ In LoG\_kernel }
The same problem of consistency for the normalization occurs here. It is in
fact worse than in the gaussian case, since I suppose that the LOG kernel does not sum to one. Besides dividing by $sigma^4$ is pointless if you normalize by the sum! Of course, kernel normalization has no impact on the edge detection since the thresholds are expressed in a relative way.

\ans Corrected, now  the code uses the PDF formula\\

\subsubsection{ In the README:}
\que you announce that:
"More than one algorithm can be applied to the same image with the same
command. For example:
edges -r 0.1 -l 3 29 0.13 molino.png
will apply Roberts' algorithm with threshold parameter 0.1, and the
Marr-Hildreth (LoG) with parameters sigma=3.00, N=29, TZC=0.13;"
You should also warn that each algorithm can be launched only once. For instance
the following call will fail:
edges -r 0.1 -r 0.2 -l 3 29 0.13 molino.png\\

\ans Explicitely said in documentation that you can't execute two algorithms at the same time,\\

### 2014-05-26 edge-detection-review-2nd-revision-v2.tex
Completed second round of review

\documentclass{ipol}
\ipolSetYear{2012}
\ipolSetMonth{06}
\ipolSetDay{06}
%\ipolSetID{arced}
\ipolSetTitle{A Review of Classic Edge Detectors}
\ipolSetAuthors{Haldo Spont\'on$^1$, Juan Cardelino$^2$, Rafael Grompone von Gioi$^3$}
\ipolSetAffiliations{%
$^1$ IIE, UdelaR, Uruguay (\texttt{haldos@fing.edu.uy})\\
$^2$ IIE, UdelaR, Uruguay (\texttt{juanc@fing.edu.uy})\\
$^3$ CMLA, ENS Cachan, France (\texttt{grompone@cmla.ens-cachan.fr})}

\usepackage{hyperref,verbatim,graphicx,amsmath,amssymb,amssymb,dsfont}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{sidecap}
\usepackage[hang,center]{subfigure}
\usepackage[table]{xcolor}
\usepackage{multicol}
\usepackage{listings}
\usepackage{color}
\usepackage{calc}
\usepackage{array}
%\usepackage{algorithm}
\usepackage{algorithmic}
\newtheorem{theorem}{Theorem}
\numberwithin{equation}{section}
\numberwithin{table}{section}
%\numberwithin{figure}{section}
\begin{document}
\bibliographystyle{ieeetr}
\lstset{
	backgroundcolor=\color[rgb]{0.94,0.94,0.94},
    tabsize=4,
    inputencoding=utf8x,
         extendedchars=\true,
         language=C,
         basicstyle=\scriptsize,
                 showtabs=false,
        showspaces=false,
        showstringspaces=false,
        identifierstyle=\ttfamily,
        keywordstyle=\color[rgb]{0,0,1},
        commentstyle=\color[rgb]{0.133,0.545,0.133},
        stringstyle=\color[rgb]{0.627,0.126,0.941},
}
% Square cells table
\newlength\celldim \newlength\fontheight \newlength\extraheight
\newcounter{sqcolumns}
\newcolumntype{S}{ @{}
  >{\centering \rule[-0.5\extraheight]{0pt}{\fontheight + \extraheight}}
  p{\celldim} @{} }
\newcolumntype{Z}{ @{} >{\centering} p{\celldim} @{} }
\newenvironment{squarecells}[1]
  {\setlength\celldim{2em}%
   \settoheight\fontheight{A}%
   \setlength\extraheight{\celldim - \fontheight}%
   \setcounter{sqcolumns}{#1 - 1}%
   \begin{tabular}{|S|*{\value{sqcolumns}}{Z|}}\hline}
% squarecells tabular goes here
  {\end{tabular}}
\newcommand\nline{\tabularnewline\hline}

@@

\begin{abstract}
In this paper some of the classic alternatives for edge detection in digital images are studied. The main idea 
behind edge detection is to find where abrupt changes in the intensity of an image have occurred. 
The first family of algorithms reviewed in this work uses the first derivative to find the changes of intensity, 
such as Sobel, Prewitt and Roberts. In the second reviewed family, second derivatives are used, for example in algorithms 
like Marr-Hildreth and Haralick. \\
Results obtained from a qualitative point of view (perceptual) and from a quantitative 
point of view (number of operations, execution time) are compared, considering different ways to convolve an 
image with a kernel (step required in some of the algorithms).
\end{abstract}

@@

% No mas link, mirar como se pone en las publicaciones nuevas. (ir a buscar el codigo a la pagina de la publicacion)
% lo mismo con la demo... sacar GIT

%% VER SI HAY UN TEXTO ESTANDAR PARA ESTO
\begin{ipolCode}
For all the algorithms reviewed, an open source C implementation is provided that can be downloaded from 
the IPOL publication of this article. An 
\href{http://dev.ipol.im/~haldos/ipol_demo/xxx_edges/}{online demonstration} is also available, where 
you can test and reproduce our results.
\end{ipolCode}

@@

% cambiar lo de segmenting images. Decir que edge detection es una de las operaciones
% basicas y mas antiguas en el procesamiento de imagenes.
% Edge detection is one of the first approaches published in the literature for 
% segmenting images. 
The basic idea of edge detection algorithms is to detect abrupt changes in image intensity. 
Detecting those changes in intensity for the purpose of finding edges in images 
can be accomplished using first or second order derivatives.

In the 70's, edge detection methods were based on using small operators 
(such as Sobel masks), attempting to compute an approximation of the
first derivative of the image \cite{Gonzalez2007Digital}. Next section describes such algorithms and serves as an introduction to a more sophisticated analysis of the edge detection process.

% en este parrafo, puede ser cambiar trough por valley
In 1980 Marr and Hildreth \cite{AIM-518} argued that intensity changes are not independent 
of image scale, so edge detection requires the use of different size 
operators. They also argued that a sudden intensity change will be seen 
as a peak (or trough) in the first derivative or, equivalently, as a zero 
crossing in the second derivative. This algorithm is presented in Section \ref{sec:second}. 
Haralick's algorithm \cite{bb20239} is an alternative approach based on the second derivative 
which is also reviewed in Section \ref{sec:second}. This algorithm has the particularity of 
proposing a model to locally approximate the image around a point; then, using this model, 
an approximation to the second derivative of the image can be calculated analytically and 
finding edges is achieved by imposing a condition over the model parameters.

@@

\section{Algorithms based on first derivative}
\label{sec:first}

Algorithms based on first derivative studied in this paper have a common scheme, with 
the only difference in the type of filtering. Figure \ref{fig:blockdiagram1} shows
a block diagram of these algorithms. \\

@@

The most usual approach to approximate the first derivative is to take the Taylor expansion of first order with
a small $h$. Thus $f'(x)$ is computed as
\begin{equation}
	f'(x) \simeq \frac{f(x+h) - f(x)}{h}.
\end{equation}
% explicar que esta pasando con el h
% en las operaciones de abajo, dejar explicito que se considera h=1
The image is composed by discrete points of coordinates $(i,j)$, so taking $x=ih$ and $y=jh$, the 
first derivative of the image is approximated, based on the intensity values ​​at points of the image, as\footnote{This approximation considerates $h=1$, so the partial derivatives can be computed as intensity difference between neighbor pixels.}:
\begin{equation}
\label{eq:roberts1}
	f_x = \frac{\partial f(x,y)}{\partial x} \cong f(i+1,j) - f(i,j)
\end{equation}
and
\begin{equation}
\label{eq:roberts2}
	f_y = \frac{\partial f(x,y)}{\partial y} \cong f(i,j+1) - f(i,j).
\end{equation}

Equations \ref{eq:roberts1} and \ref{eq:roberts2} can be implemented for all values of $x$ and $y$
by filtering the image $f(x,y)$ with the 1-D masks in Figure \ref{fig:1dmasks}. %But when finding 
%diagonal edges is desired, 2-D masks are needed. 
The \textit{Roberts operators} are one of the earliest 
attempts to use 2-D masks for this purpose. These operators are based on computing the diagonal 
diferences implemented by filtering an image with the masks in Figure \ref{fig:roberts}. By convention 
in these figures, x-coordinates grow from left to right and y-coordinates grow top-down. It is also 
usual to scale the mask values, in order to have unit $L_2$ norm.

@@

\begin{SCfigure}[2][!h]
	\centering
	\begin{squarecells}{1}
		-1   \nline
		1  \nline
	\end{squarecells}
	\quad
	\begin{squarecells}{2}
		-1 & 1   \nline
	\end{squarecells}
	\caption{One-dimensional normalized masks used to implement equations \ref{eq:roberts1} and \ref{eq:roberts2}.}
	\label{fig:1dmasks}
\end{SCfigure}

\begin{SCfigure}[1][!h]
	\centering
	\begin{squarecells}{2}
		-1 &  0  \nline
		0 & 1  \nline
	\end{squarecells}
	\quad
	\begin{squarecells}{2}
		0  & -1  \nline
		1 & 0  \nline
	\end{squarecells}
	\caption{Normalized \textit{Roberts cross-gradient} 2-D masks.}
	\label{fig:roberts}
\end{SCfigure}

Figure \ref{fig:1dmasks} shows the simplest way to compute derivatives, but Roberts in his article proposes
to compute them as shown in Figure \ref{fig:roberts}. In order to use the same convolution code for all algorithms, our implementation uses $3\times3$ matrices, adding a row and a column of zeros to the matrices in Figure \ref{fig:roberts}, what produces the same result.

@@

The simplest digital approximation to the partial derivatives using masks of size $3\times3$ are obtained 
by taking the difference between the third and first rows (or columns) of the $3\times3$ region. The
difference between the third and first rows approximates the derivative in the x-direction, and 
the difference between the third and first columns approximates the derivative in the y-direction.
These approximations can be implemented by filtering the image with the two masks in Figure \ref{fig:prewitt}.
These masks are called \textit{Prewitt operators}.

\begin{SCfigure}[1][!h]
	\centering
	\begin{squarecells}{3}
		$-\frac{1}{6}$ 	& $-\frac{1}{6}$ 	& $-\frac{1}{6}$	\nline
		0 			& 0			& 0			\nline
		$\frac{1}{6}$ 	& $\frac{1}{6}$ 	& $\frac{1}{6}$	\nline
	\end{squarecells}
	\quad
	\begin{squarecells}{3}
		$-\frac{1}{6}$ 	& 0 	& $\frac{1}{6}$	\nline
		$-\frac{1}{6}$	& 0	& $\frac{1}{6}$	\nline
		$-\frac{1}{6}$ 	& 0 	& $\frac{1}{6}$	\nline
	\end{squarecells}
	\caption{Normalized \textit{Prewitt} 2-D masks of size $3\times3$.}
	\label{fig:prewitt}
\end{SCfigure}

These masks can be obtained (beyond normalization) as the convolution of a horizontal derivation mask 
$[-1\ 0\ 1]$ with a vertically moving average $[1\ 1\ 1]^T$, and vice versa. Hence, these operators have 
smoothing properties in the direction orthogonal to the gradient.

@@

A slight variation of the Prewitt operators uses more weight on the central coefficients of the 
difference. It can be shown that using double weight in the center location provides better image smoothing. This
variation is implemented using masks in Figure \ref{fig:sobel}. These operators are called 
\textit{Sobel operators}.

Sobel masks can be seen (beyond normalization) as the convolution of a horizontal derivation mask 
$[-1\ 0\ 1]$ with a vertical smoothing filter $[1\ 2\ 1]^T$ (closer to a Gaussian response than Prewitt), and vice versa. 
Hence, these operators have better smoothing properties, as mentioned in the preceding paragraph.

\begin{SCfigure}[1][!h]
	\centering
	\begin{squarecells}{3}
		$-\frac{1}{8}$ 	& $-\frac{1}{4}$ 	& $-\frac{1}{8}$	\nline
		0 			& 0			& 0			\nline
		$\frac{1}{8}$ 	& $\frac{1}{4}$ 	& $\frac{1}{8}$	\nline
	\end{squarecells}
	\quad
	\begin{squarecells}{3}approximate
		$-\frac{1}{8}$ 	& 0 	& $\frac{1}{8}$	\nline
		$-\frac{1}{4}$	& 0	& $\frac{1}{4}$	\nline
		$-\frac{1}{8}$ 	& 0 	& $\frac{1}{8}$	\nline
	\end{squarecells}
	\caption{Normalized \textit{Sobel} 2-D masks of size $3\times3$.}
	\label{fig:sobel}
\end{SCfigure}

The computational difference between Prewitt and Sobel masks is not an issue. It is preferable to 
use Sobel operators, because they are better localized, and their filter are also less aliased, 
because of the weighted shape of $[1\ 2\ 1]$.

@@

As mentioned before, edges can be seen as abrupt changes in intensity, i.e.\ higher values of gradient.
An example of this behavior is shown in Figure \ref{fig:profiles3d}, where gradient was computed using the Sobel operators.

@@

The two algorithms presented in this section (Marr-Hildreth \cite{AIM-518} [1980] and Haralick \cite{bb20239} [1987]) 
are based on the second derivative of the image, and both take steps to reduce noise before 
detecting edges in the image.

>>>>

\documentclass{ipol}
\ipolSetYear{2012}
\ipolSetMonth{06}
\ipolSetDay{06}
%\ipolSetID{arced}
\ipolSetTitle{A Review of Classic Edge Detectors}
\ipolSetAuthors{Haldo Spont\'on$^1$, Juan Cardelino$^2$}
\ipolSetAffiliations{%
$^1$ IIE, UdelaR, Uruguay (\texttt{haldos@fing.edu.uy})\\
$^2$ IIE, UdelaR, Uruguay (\texttt{juanc@fing.edu.uy})}

\usepackage{hyperref,verbatim,graphicx,amsmath,amssymb,amssymb,dsfont}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{sidecap}
\usepackage[hang,center]{subfigure}
\usepackage[table]{xcolor}
\usepackage{multicol}
\usepackage{listings}
\usepackage{color}
\usepackage{calc}
\usepackage{array}
%\usepackage{algorithm}
\usepackage{algorithmic}
\newtheorem{theorem}{Theorem}
\numberwithin{equation}{section}
\numberwithin{table}{section}
%\numberwithin{figure}{section}
\usepackage{marginnote}
\newcounter{mynote}% a new counter for use in margin notes
\usepackage{jfc}
\begin{document}

\lstset{
	backgroundcolor=\color[rgb]{0.94,0.94,0.94},
    tabsize=4,
    inputencoding=utf8x,
         extendedchars=\true,
         language=C,
         basicstyle=\scriptsize,
                 showtabs=false,
        showspaces=false,
        showstringspaces=false,
        identifierstyle=\ttfamily,
        keywordstyle=\color[rgb]{0,0,1},
        commentstyle=\color[rgb]{0.133,0.545,0.133},
        stringstyle=\color[rgb]{0.627,0.126,0.941},
}
% Square cells table
\newlength\celldim \newlength\fontheight \newlength\extraheight
\newcounter{sqcolumns}
\newcolumntype{S}{ @{}
  >{\centering \rule[-0.5\extraheight]{0pt}{\fontheight + \extraheight}}
  p{\celldim} @{} }
\newcolumntype{Z}{ @{} >{\centering} p{\celldim} @{} }
\newenvironment{squarecells}[1]
  {\setlength\celldim{2em}%
   \settoheight\fontheight{A}%
   \setlength\extraheight{\celldim - \fontheight}%
   \setcounter{sqcolumns}{#1 - 1}%
   \begin{tabular}{|S|*{\value{sqcolumns}}{Z|}}\hline}
% squarecells tabular goes here
  {\end{tabular}}
\newcommand\nline{\tabularnewline\hline}

@@

\begin{abstract}
In this paper some of the classic alternatives for edge detection in digital images are studied. The main idea 
of edge detection algorithms is to find where abrupt changes in the intensity of an image have occurred. 
The first family of algorithms reviewed in this work uses the first derivative to find the changes of intensity, 
such as Sobel, Prewitt and Roberts. In the second reviewed family, second derivatives are used, for example in algorithms 
like Marr-Hildreth and Haralick. \\
Results obtained from a qualitative point of view (perceptual) and from a quantitative 
point of view (number of operations, execution time) are compared, considering different ways to convolve an 
image with a kernel (step required in some of the algorithms).
\end{abstract}

@@

\begin{ipolCode}
For all the algorithms reviewed, an open source C implementation is provided that can be downloaded from 
the IPOL publication of this article. An 
\href{http://dev.ipol.im/~haldos/ipol_demo/xxx_edges/}{online demonstration}\footnote{\url{http://dev.ipol.im/~haldos/ipol_demo/xxx_edges/}} is also available, where 
you can test and reproduce our results.
\end{ipolCode}

@@

Edge detection is one of the oldest and most basic operations operations in image processing, which is often used as a basic building block for more complex algorithms.  for 
. The basic idea of edge detection is to detect abrupt changes in image intensity. 
Detecting those changes can be accomplished using first or second order derivatives. \\

In the 70's, edge detection methods were based on using small operators 
(such as Sobel masks), attempting to compute an approximation of the
first derivative of the image \cite{Gonzalez2007Digital}. Section ~\ref{sec:first} describes such algorithms 
and serves as an introduction to a more sophisticated 
analysis of the edge detection process.

% en este parrafo, puede ser cambiar trough por valley
In 1980 Marr and Hildreth \cite{AIM-518} argued that intensity changes are not independent 
of image scale, so edge detection requires the use of different size 
operators. They also argued that a sudden intensity change will be seen 
as a peak (or valley) in the first derivative or, equivalently, as a zero 
crossing in the second derivative. This algorithm is presented in Section \ref{sec:second}. 
Haralick's algorithm \cite{bb20239} is an alternative approach based on the second derivative 
which is also reviewed in Section \ref{sec:second}. This algorithm has the particularity of 
proposing a model to locally approximate the image around a point; then, using this model, 
an approximation to the second derivative of the image can be calculated analytically and 
finding edges is achieved by imposing a condition over the model parameters.

@@

\section{Algorithms based on the first derivative}
\label{sec:first}

Algorithms based on first derivatives studied in this paper share a common structure, with the only difference  in the type of filtering used to compute those derivatives. Figure \ref{fig:blockdiagram1} shows a block diagram of that common structure. \myn{\label{correction_a:first_derivative:first_deriv_rephrase}\\

@@

\myn{\label{correction_a:first_derivative:taylor}}The most usual approach to approximate the first derivative is to use a the first order Taylor expansion with a small value of $h$. Thus $f'(x)$ is computed as
\begin{equation}
	f'(x) \simeq \frac{f(x+h) - f(x)}{h}.\\
\end{equation}
\myn{\label{correction_a:first_derivative:discretization}} Digital images are commonly seen as a discretization of a continuos image, where a pixel is evenly sample on a grid. If we denote the grid sizes by $\Delta x$ and $\Delta y$, the continuous coordinates $x$  and $y$ can be written as $x=i\Delta x$ and $y=i\Delta y$. When no information about the spatial sampling is available, the size of the grid it is commonly assumed to be $\Delta x=\Delta y=1$.\\
Thus, in the discrete space the first derivative of the image is computed as:
\begin{equation}
\label{eq:roberts1}
	f_x = \frac{\partial f(x,y)}{\partial x} \cong f(i+1,j) - f(i,j)
\end{equation}
and
\begin{equation}
\label{eq:roberts2}
	f_y = \frac{\partial f(x,y)}{\partial y} \cong f(i,j+1) - f(i,j).
\end{equation}

\myn{\label{correction_a:first_derivative:diagonal edges}} Equations \ref{eq:roberts1} and \ref{eq:roberts2} can be implemented for all values of $x$ and $y$ by filtering the image $f(x,y)$ with the 1-D masks shown in Figure \ref{fig:1dmasks}. However, in order to be able to compute diagonal edges, 2-D masks are needed. \\
The \textit{Roberts operators} are one of the earliest 
attempts to use 2-D masks for this purpose. These operators are based on computing the diagonal \tcom{differences} \myn{\label{correction_a:typo}} implemented by filtering an image with the masks in Figure \ref{fig:roberts}. By convention 
in these figures, x-coordinates grow from left to right and y-coordinates grow top-down. It is also 
usual to scale the mask values, in order to have gain equal to $1$. \\

@@

\begin{SCfigure}[2][!h]
	\centering
	\begin{squarecells}{1}
		-1   \nline
		1  \nline
	\end{squarecells}
	\quad
	\begin{squarecells}{2}
		-1 & 1   \nline
	\end{squarecells}
	\caption{One-dimensional masks used to implement equations \ref{eq:roberts1} and \ref{eq:roberts2}.}
	\label{fig:1dmasks}
\end{SCfigure}

\begin{SCfigure}[1][!h]
	\centering
	\begin{squarecells}{2}
		-1 &  0  \nline
		0 & 1  \nline
	\end{squarecells}
	\quad
	\begin{squarecells}{2}
		0  & -1  \nline
		1 & 0  \nline
	\end{squarecells}
	\caption{\textit{Roberts cross-gradient} 2-D masks.}
	\label{fig:roberts}
\end{SCfigure}

Figure \ref{fig:1dmasks} shows the simplest way to compute derivatives, but Roberts \cite{roberts1963machine} proposes
to compute them as shown in Figure \ref{fig:roberts}. In order to use the same convolution code for all algorithms, our implementation uses $3\times3$ matrices, adding a row and a column of zeros to the matrices in Figure \ref{fig:roberts}, what produces the same result.

@@

The simplest digital approximation to the partial derivatives using masks of size $3\times3$ are obtained 
by taking the difference between the third and first rows (or columns) of the $3\times3$ region. The
difference between the third and first rows approximates the derivative in the x-direction, and 
the difference between the third and first columns approximates the derivative in the y-direction.
These approximations can be implemented by filtering the image with the two masks in Figure \ref{fig:prewitt}.
These masks are called \textit{Prewitt operators} \cite{prewitt1970object}.

\begin{SCfigure}[1][!h]
	\centering
	\begin{squarecells}{3}
		$-\frac{1}{3}$ 	& $-\frac{1}{3}$ 	& $-\frac{1}{3}$	\nline
		0 			& 0			& 0			\nline
		$\frac{1}{3}$ 	& $\frac{1}{3}$ 	& $\frac{1}{3}$	\nline
	\end{squarecells}
	\quad
	\begin{squarecells}{3}
		$-\frac{1}{3}$ 	& 0 	& $\frac{1}{3}$	\nline
		$-\frac{1}{3}$	& 0	& $\frac{1}{3}$	\nline
		$-\frac{1}{3}$ 	& 0 	& $\frac{1}{3}$	\nline
	\end{squarecells}
	\caption{Normalized \textit{Prewitt} 2-D masks of size $3\times3$.}
	\label{fig:prewitt}
\end{SCfigure}

\myn{\label{correction_a:first_derivative:sobel}} The left mask can be constructed (up to a scale factor) as the convolution of two filters: a vertical derivative 
$[-1\ 0\ 1]$ and an horizontal moving average $[1\ 1\ 1]^T$. The same reasoning could be applied to the right mask. Hence, these operators can be interpreted as the consecutive application of an horizontal low pass filter with a vertical derivative filter. Thus, they show smoothing properties in the direction orthogonal to the gradient.

@@

A slight variation of the Prewitt operators which use more weight on the central coefficients of the 
difference. It can be shown that using more weight in the center location provides better image smoothing. This
variation is implemented using masks shown in Figure \ref{fig:sobel}. These operators are called 
\textit{Sobel operators}.

\begin{SCfigure}[1][!h]
	\centering
	\begin{squarecells}{3}
		$-\frac{1}{4}$ 	& $-\frac{1}{2}$ 	& $-\frac{1}{4}$	\nline
		0 			& 0			& 0			\nline
		$\frac{1}{4}$ 	& $\frac{1}{2}$ 	& $\frac{1}{4}$	\nline
	\end{squarecells}
	\quad
	\begin{squarecells}{3}
		$-\frac{1}{4}$ 	& 0 	& $\frac{1}{4}$	\nline
		$-\frac{1}{2}$	& 0	& $\frac{1}{2}$	\nline
		$-\frac{1}{4}$ 	& 0 	& $\frac{1}{4}$	\nline
	\end{squarecells}
	\caption{\textit{Sobel} 2-D masks of size $3\times3$.}
	\label{fig:sobel}
\end{SCfigure}

Sobel masks can be seen (up to a  scale factor) as the convolution of a horizontal derivation mask 
$[-1\ 0\ 1]$ with a vertical smoothing filter $[1\ 2\ 1]$ (closer to a Gaussian response than Prewitt), and vice versa. 
Hence, these operators have better smoothing properties, as mentioned in the preceding paragraph. \\

The computational cost of applying Prewitt and Sobel masks is exactly the same. Thus, it is preferable to 
use Sobel operators, because edges are better localized, and their filter are also less aliased, because of the weighted shape of $[1\ 2\ 1]$.

@@

As mentioned before, edges can be seen as abrupt changes in intensity, i.e.\ higher values of gradient.
An example of this behavior is shown in Figure \ref{fig:profiles3d}, where gradient was computed using Sobel operators.

@@

The two algorithms presented in this section (Marr-Hildreth \cite{AIM-518} and Haralick \cite{bb20239}) 
are based on the second derivative of the image, and both take steps to reduce noise before 
detecting edges in the image.
